Quantum H theorem, variational entropy, and relaxation processes

### 2021-01-25 tex/introduction.tex
Typos: intro

In addition, some aspects regarding the classical $H$-theorem and the
Boltzmann $H$-functional require to be revised, for the purpose of improving their mutual consistency.
For example, the modification of the $H$-theorem to include phenomena stemming from stochastic
trajectories, violations of the second law of thermodynamics, the relation
between Shannon's measure of information and the Boltzmann's entropy, 
and calculation of thermodynamical quantities and thermalization for some systems
\cite{bib:gorban2014,bib:li2019,bib:gring2012,bib:nemilov2018,bib:wang2014}.

>>>>

In addition, some aspects regarding the classical $H$-theorem and the
Boltzmann $H$-functional require to be revised, for the purpose of improving their mutual consistency.
For example, the modification of the $H$-theorem to include phenomena stemming from stochastic
trajectories, violations of the second law of thermodynamics, the relation
between Shannon's measure of information and the Boltzmann's entropy, 
and the calculation of thermodynamical quantities and thermalization of certain systems
\cite{bib:gorban2014,bib:li2019,bib:gring2012,bib:nemilov2018,bib:wang2014}.
